### 2014-10-17 simulation.Rmd
Comparing results to simulation.

## Fitted parameter values
```{r, echo=FALSE, results="asis"}
par_df = data.frame(value = model@results[["par"]], row.names = names(model@results[["par"]]))
pandoc.table(par_df, style="rmarkdown")
par_df$names = row.names(par_df)
par_df = par_df[grep("->", par_df$names),]
ggplot(par_df, aes(x = names, y = value)) +
    geom_bar(stat = "identity", fill="white", color="gray") +
    theme(axis.text.x = element_text(angle = 90))
```

```{r}
model
```

@@

## if present, MCMC traces

## ... and posterior marginal distributions.

>>>>

## Fitted parameter values
```{r, echo=FALSE, results="asis"}
mr_compare <- data.frame(fit=model@mutrates / time)
mr_compare$names <- rownames(mr_compare)
simvalues= data.frame(names=mutnames(simseq.config$tip$mutpats), 
                      simulated=simseq.config$tip$mutrates)
mr_compare <- merge(simvalues, mr_compare)
pandoc.table(mr_compare, style="rmarkdown")
```

The corresponding plot, where bars are the simulated values, and points are the fit values:
```{r, echo=FALSE, results="asis"}
ggplot(mr_compare, aes(x=names)) +
    geom_bar(aes(y=fit), stat = "identity", fill="white", color="gray") + 
    geom_point(aes(y=simulated)) +
    theme(axis.text.x = element_text(angle = 90),
          axis.title.y = element_blank())
```

@@
